### 2019-04-05 papers/journal/encoding.tex
removed unwanted refernce

%\externaldocument{sat-table}
%\externaldocument{smt-table}
%\externaldocument{qbf-table}
\noindent In the previous section, we have discussed four problems, $\fbmc$ search, $\fsmt$ search, $\fqbf$ search and synthesis problem.
%
In this section we will present encodings for each of them.
%
Although the underlying technique for $\fbmc$ and $\fsmt$ search varies, the encoding is very similar. 
%
So, instead of presenting both 
%$\fsmt$ search, $\fbmc$ search, $\fqbf$ search and synthesis problems.
%
we will start with the complete $\fsmt$ search encoding and present only the relevant part of the the $\fbmc$ encoding to show a contrast.
%contrast with the $\fbmc$ encoding.

@@

\noindent Our first attempt was to encode the existential condition check as a $\fbmc$ search problem~\cite{shukla2017discovering}.
%
%In this section we will present the $\fbmc$ encoding of the same.
%
Although the techniques used for $\fbmc$ and $\fsmt$ is very different because we are not unrolling the complete program in the case of $\fbmc$, the encoding is not considerably different.
% 
The $\fbmc$ search encoding differs with the presented $\fsmt$ encoding in the way variables are represented and how we encode reachability (both for the stability and connectivity).  
%
Here, we will only present the stability encoding.
%the rest of the encodings are similar to the one presented in the previous section, Section~\ref{enc:smt}.

>>>>

%\externaldocument{sat-table}
%\externaldocument{smt-table}
%\externaldocument{qbf-table}
\noindent In the previous section, we have discussed four problems, $\fbmc$ search, $\fsmt$ search, $\fqbf$ search and synthesis problem.
%
In this section we will present encodings for each of them.
%
Although the underlying technique for $\fbmc$ and $\fsmt$ search varies, the encoding is very similar. 
%
So, instead of presenting serially the complete encoding of both, 
%$\fsmt$ search, $\fbmc$ search, $\fqbf$ search and synthesis problems.
%
we will start with the complete $\fsmt$ search encoding and present only the relevant part of the the $\fbmc$ encoding to show a contrast.
%contrast with the $\fbmc$ encoding.

@@

\noindent Our first attempt was to encode the existential condition check as a $\fbmc$ search problem~\cite{shukla2017discovering}.
%
%In this section we will present the $\fbmc$ encoding of the same.
%
%Although the techniques used for $\fbmc$ and $\fsmt$ is very different because we are 
%In $\fbmc$ we only partially unroll the program to check for the solutions within that subset. 
%in the case of $\fbmc$, the encoding is not considerably different.
% 
In comparison to $\fsmt$, the $\fbmc$ search encodes reachability (both for the stability and connectivity) differently.  
%]
Here, we will only present the stability encoding.
%the rest of the encodings are similar to the one presented in the previous section, Section~\ref{enc:smt}.
